---
title: "Mini Literature Analysis"
format: html
---



## Introduction

### About the data
This data set contains North Pole Environmental Observatory Bottle Chemistry data. This data set includes diverse measurements of seawater chemistry along with supporting conductivity, temperature, and depth (CTD) data from the Arctic Ocean near the North Pole. This data was downloaded from the [ADC](https://arcticdata.io/catalog/view/doi:10.18739/A25T3FZ8X)

### Setup
```{r}
library(readr)
```

### Read Data

```{r}
bg_chem <- read_csv("data/BGchem2008data.csv")
```

Exploring data
```{r}
colnames(bg_chem)
summary(bg_chem)
unique(bg_chem$Date)
```

## Analysis



### Calculate Summary Statistics

```{r}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
amm <- mean(bg_chem$NH4)
phos <- mean(bg_chem$P)

```


### Calculate the mean Readfield ratio

```{r}
ratio <-(nitrate + nitrate + amm)/phos
```


### Plot Ratio
```{r}
plot(bg_chem$P, bg_chem$NO3 + bg_chem$NO2 + bg_chem$NH4)
```


## Conclusion


The Redfield ratio is `r round(ratio)`







